### 2021-06-11 paper/report.tex
Add estimate of the costs of the winter lockdown.

In order to better understand the contributions  of rapid tests, vaccinations, and of
seasonality on the evolution of infections in 2021,
Figure~\ref{fig:2021_scenarios_broad} considers various scenarios. NPIs are always the
same as in the baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the
model fit (the blue line, same as in Figure~\ref{fig:aggregated_fit}), a scenario
without any of the three factors (red line), and three scenarios turning these factors
off one by one. Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total
infections in the model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley
values\comment[id=HM]{Need reference} to decompose the difference in total infections
between the scenario without any of the three factors and our main specification.

@@

Despite these large effects, the results on testing likely understate the benefits. Disadvantaged groups of the population are less likely to be reached by testing campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We should get the raw data, btw.} at the same time they have a higher risk to contract CoViD-19.\citet{RKI-Corona-Monitoring-Bundesweit}\comment[id=HM]{\url{https://www.rki.de/DE/Content/Gesundheitsmonitoring/Studien/lid/Ergebnisse.pdf}} Mandatory tests at school and at the workplace will extend more into these groups. The same goes for individuals who exhibit a low level of compliance with CoViD-19-related regulations. Our analysis has shown that in the transition path to high levels of vaccination and possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes at a fraction of the cost. A day of the winter lockdown in Germany is estimated to have cost XXX~Euros. In early June 2021, retail prices for self-administered rapid tests are frequently less than 1~Euro.

>>>>

In order to better understand the contributions  of rapid tests, vaccinations, and of
seasonality on the evolution of infections in 2021,
Figure~\ref{fig:2021_scenarios_broad} considers various scenarios. NPIs are always the
same as in the baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the
model fit (the blue line, same as in Figure~\ref{fig:aggregated_fit}), a scenario
without any of the three factors (red line), and three scenarios turning these factors
off one by one. Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total
infections in the model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley
values \citep{Shapley2016} to decompose the difference in total infections
between the scenario without any of the three factors and our main specification.

@@

Despite these large effects, the results on testing likely understate the benefits.
Disadvantaged groups of the population are less likely to be reached by testing
campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We
should get the raw data, btw.} at the same time they have a higher risk to contract
CoViD-19.\citet{RKI-Corona-Monitoring-Bundesweit}\comment[id=HM]{\url{https://www.rki.de/DE/Content/Gesundheitsmonitoring/Studien/lid/Ergebnisse.pdf}}
Mandatory tests at school and at the workplace will extend more into these groups. The
same goes for individuals who exhibit a low level of compliance with CoViD-19-related
regulations. Our analysis has shown that in the transition path to high levels of
vaccination and possibly thereafter, large-scale rapid testing can substitute for some
NPIs. This comes at a fraction of the cost. A day of the winter lockdown in Germany is
estimated to have cost 6.25~billion~Euros.\cite{Dorn2020}\comment[id=K]{This is a
prediction by the ifo Instute back from March 2020 assuming a 2 month lockdown. I did not
find anything citable that is earlier. I did find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown} In early June 2021, retail prices
for self-administered rapid tests are frequently less than 1.5~Euro.\footnote{Cheapest on
\href{https://amazon.de}{Amazon} on June 11th, 2021.}
